### 2017-01-15 sec-results.tex
Add results about mean rank comparisons.

>>>>

To quantify this finding, we perform the following experiment. First, we
select all students from \textretrieval{} who completed all of the quizzes
$\mathbf{L}_q \subset \mathbf{L}$. This gives us 1,985 students along with
their average quiz score. We then create a ranked list of the students in
$\mathbf{L}_q$ by sorting them by their ``preference'' for a specific
latent state
\begin{equation}
  p_\ell(i) = \frac{\sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(i)}
  {\sum_{j=1}^{K} \sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(j)}
\end{equation}
where $\mathbf{o}_\ell$ is the list of action sequences for student $\ell$
and $\gamma$ is defined as before and computed using the Baum-Welch
algorithm. We can now compare the average rank in this list for both
the ``perfect'' student group and the ``low'' student group: a useful state
for distinguishing the two groups should result in a ranked list with
statistically significant differences in average rank between the two
groups. Our results are summarized in Table~\ref{table:mean-rank}. Indeed,
we discover that states 1 and 2 are useful for teasing apart these two
groups: state 1 ranks students in the ``low'' group significantly higher
than those in the ``perfect'' group, and state 2 does the opposite and
prefers students in the ``perfect'' group to those in the ``low'' group.

\begin{table}
  \centering
  \begin{tabular}{r|rrrr}
    \textbf{Group} & \textbf{State 0} & \textbf{State 1}^\dagger &
    \textbf{State 2}^\dagger & \textbf{State 3}\\\hline
    \textbf{Perfect} & 975.3  & 1001.5 & 999.0  & 1056.5\\
    \textbf{Low}     & 1024.9 & 816.4  & 1230.5 & 1161.2\\
  \end{tabular}
  \caption{Average rank for ``perfect'' and ``low'' student groups in the
  ranked lists associated with the four latent states found by a TL-HMM.
  $\dagger$ indicates statistically significant different mean ranks at $p
  < 0.01$ according to an unpaired $t$-test.}
  \label{table:mean-rank}
\end{table}
